---
title: "PH.140.644_HW3"
author: "Kunyu An"
output:
  pdf_document:
    toc_depth: 2
    latex_engine : xelatex
  html_document:
    toc_depth: '2'
    df_print: paged
header-includes:
- \usepackage{amsmath,latexsym,amsfonts,amsthm,cleveref}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


```{r load_libraries,include=FALSE}
library(tidyverse)
library(ISLR)
library(MASS) 
library(class)
```

In this project, my goal is to analyse `NHANES 2003-2004` data and build a model to predict the mortality status for participants 50 years and older. I plan to divid this project into three parts. The first is the data preprocessing part, in which I will clean the data, determin the predictors as well as split the training and testing sets. The second part is to build a classification model to do the prediction. Finally, I will explore and preforme some statistical analysis on the results.

### Data Preprocessing

- we first load the dataset.
```{r}
load(file = "nhanes2003-2004.Rda")
```


