---
title: "PH.140.644_HW3"
author: "Kunyu An"
output:
  pdf_document:
    toc_depth: 2
    latex_engine : xelatex
  html_document:
    toc_depth: '2'
    df_print: paged
header-includes:
- \usepackage{amsmath,latexsym,amsfonts,amsthm,cleveref}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


```{r load_libraries,include=FALSE}
library(tidyverse)
library(ISLR)
library(MASS) 
library(class)
```

In this project, my goal is to analyse `NHANES 2003-2004` data and build a model to predict the mortality status for participants 50 years and older. I plan to divid this project into three parts. The first is the data preprocessing part, in which I will clean the data, determin the predictors as well as split the training and testing sets. The second part is to build a classification model to do the prediction. Finally, I will explore and preforme some statistical analysis on the results.

### Data Preprocessing

- we first load the dataset.
```{r}
load(file = "nhanes2003-2004.Rda")
```

```{r}
predictors <- c("RIDAGEYR", "RIAGENDR", "BPQ010", "BPQ060", "SMQ040", "DIQ010", "DIQ050", "DIQ090", "MCQ010", "MCQ053", "MCQ160A", "MCQ160B", "MCQ160K", "MCQ160L", "BMXWAIST", "MCQ160M", "MCQ220", "MCQ245A", "MCQ250A", "MCQ250B", "MCQ250C", "MCQ250E", "MCQ250F", "MCQ250G", "MCQ265", "SSQ011", "SSQ051", "WHQ030", "WHQ040", "LBXRDW", "HSD010", "BPXPULS", "BPXML1", "VIQ200", "BMXBMI", "BPXSY1", "BPXDI1")
```
```{r}
above50 <- nhanes2003_2004[is.na(nhanes2003_2004$mortstat)!=TRUE,]
```