---
title: "PH.140.644_HW2"
author: "Kunyu An"
output:
  pdf_document:
    toc_depth: 2
    latex_engine : xelatex
  html_document:
    toc_depth: '2'
    df_print: paged
header-includes:
- \usepackage{amsmath,latexsym,amsfonts,amsthm,cleveref}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


```{r load_libraries,include=FALSE}
library(ISLR)
library(MASS) 
library(class)
```

## Chapter 5

### Q1
\begin{equation}
\begin{split}
Var(\alpha X, (1-\alpha)Y)&=\alpha^{2}\sigma_{X}^{2}+2\alpha(1-\alpha)\sigma_{XY}+(1-\alpha)^{2}\sigma_{Y}^{2}\\
&=(\sigma_{X}^{2}-2\sigma_{XY}+\sigma_{Y}^{2})\alpha^{2}+2(\sigma_{XY}-\sigma_{Y}^{2})\alpha+\sigma_{Y}^{2}
\end{split}
\end{equation}
Let
\begin{equation}
\frac{\partial Var(\alpha X, (1-\alpha)Y)}{\partial \alpha}=2(\sigma_{X}^{2}-2\sigma_{XY}+\sigma_{Y}^{2})\alpha+2(\sigma_{XY}-\sigma_{Y}^{2})=0
\end{equation}
We have, 
\begin{equation}
\alpha = \frac{\sigma_{Y}^{2} - \sigma_{XY}}{\sigma_{X}^{2} + \sigma_{Y}^{2} - 2 \sigma_{XY}}    
\end{equation}
Since we also have
\begin{equation}
\frac{\partial^{2} Var(\alpha X, (1-\alpha)Y)}{\partial \alpha^{2}}=2(\sigma_{X}^{2}-2\sigma_{XY}+\sigma_{Y}^{2})\geq 0
\end{equation}
Therefore, when $\alpha = \frac{\sigma_{Y}^{2} - \sigma_{XY}}{\sigma_{X}^{2} + \sigma_{Y}^{2} - 2 \sigma_{XY}}$, $Var(\alpha X, (1-\alpha)Y)$ reaches its minimum.

### Q3 
We now review k-fold cross-validation.

**a.**Explain how k-fold cross-validation is implemented.

For k-fold cross validation, we first need to divide the sample randomly into k equal-size and non-overlapping groups. Then, every time we use one group as the validation set and the rest as a whole to be the training set. Finally we can compute the testing error by averaging over the statistics of interest in k experiments.

**b.**what are the advantages and disadvantages of k-fold cross-
validation relative to:

*i. The validation set approach?*

1. The k-fold cross validation has a much lower variability than the validation set approach. 

2. All the data is used to both train and test model performance for k-fold CV.

3. The validation set approach is much easier to understand and to preform. A model is only trained once and tested once. In k-fold CV, k models will be trained and tested.

*ii. LOOCV?*

1. k-fold cross validation is less computationally demanding then LOOCV.
2. LOOCV has higher variance than k-fold CV.

### Q5
In Chapter 4, we used logistic regression to predict the probability of `default` using `income` and `balance` on the `Default` data set. We will now estimate the test error of this logistic regression model using the validation set approach. Do not forget to set a random seed before beginning your analysis.

**a.** Fit a logistic regression model that uses `income` and `balance` to predict `default`.

```{r}
library(ISLR)
attach(Default)
set.seed(1)
fit.glm = glm(default ~ income + balance, data = Default, family = "binomial")
summary(fit.glm)
```
**b.** Using the validation set approach, estimate the test error of this model. In order to do this, you must perform the following steps:

*i. Split the sample set into a training set and a validation set.*
```{r}
smp_siz <- floor(0.7*nrow(Default))
idx <- sample(seq_len(nrow(Default)),size = smp_siz)
train<-Default[idx,]
test<-Default[-idx,]
```
*ii. Fit a multiple logistic regression model using only the training observations.*
```{r}
fit.glm = glm(default ~ income + balance, data = train, family = "binomial")
summary(fit.glm)
```
*iii. Obtain a prediction of default status for each individual in the validation set by computing the posterior probability of default for that individual, and classifying the individual to the* `default` *category if the posterior probability is greater than 0.5.*
```{r}
probs.glm=predict(fit.glm,newdata = test, type='response')
pred.glm=rep('Yes',length(probs.glm))
pred.glm[probs.glm<0.5]='No'
```
*iv. Compute the validation set error, which is the fraction of the observations in the validation set that are misclassified.*
```{r}
mean(pred.glm != test$default)
```

**c.** Repeat the process in (b) three times, using three different splits of the observations into a training set and a validation set. Comment on the results obtained.

```{r}
errors <- c()
set.seed(1)
for(i in 1:3){
  smp_siz <- floor(0.7*nrow(Default))
  idx <- sample(seq_len(nrow(Default)),size = smp_siz)
  train <- Default[idx,]
  test <- Default[-idx,]
  fit.glm = glm(default ~ income + balance, data = train, family = "binomial")
  probs.glm = predict(fit.glm,newdata = test, type='response')
  pred.glm = rep('Yes',length(probs.glm))
  pred.glm[probs.glm<0.5]='No'
  errors[i] <- mean(pred.glm != test$default)
}
errors
```
**We can see that the validation set error varies as the training set varies but they are not very far away from each other.**

**d.** Now consider a logistic regression model that predicts the prob- ability of `default` using `income`, `balance`, and a dummy variable for `student`. Estimate the test error for this model using the validation set approach. Comment on whether or not including a dummy variable for `student` leads to a reduction in the test error rate.
```{r}
smp_siz <- floor(0.7*nrow(Default))
idx <- sample(seq_len(nrow(Default)),size = smp_siz)
train <- Default[idx,]
test <- Default[-idx,]
fit.glm = glm(default ~ income + balance + student, data = train, family = "binomial")
probs.glm = predict(fit.glm,newdata = test, type='response')
pred.glm = rep('Yes',length(probs.glm))
pred.glm[probs.glm<0.5]='No'
mean(pred.glm != test$default)
```
**The error is very close to previous ones. Thus we can say that including a dummy variable for student does not lead to a reduction in the test error rate.**

### Q6
We continue to consider the use of a logistic regression model to predict the probability of `default` using `income` and `balance` on the `Default` data set. In particular, we will now compute estimates for the standard errors of the `income` and `balance` logistic regression coefficients in two different ways: (1) using the bootstrap, and (2) using the standard formula for computing the standard errors in the `glm()` function. Do not forget to set a random seed before beginning your analysis.

**(a).**
Using the summary() and glm() functions, determine the estimated standard errors for the coefficients associated with income and balance in a multiple logistic regression model that uses both predictors.
```{r}
set.seed(1)
attach(Default)
fit.glm <- glm(default ~ income + balance, data = Default, family = "binomial")
summary(fit.glm)
```
**The estimated standard errors for the coefficients associated with income and balance are** $4.985e-06$ and $2.274e-04$.

**(b).**
Write a function, `boot.fn()`, that takes as input the `Default` data set as well as an index of the observations, and that outputs the coefficient estimates for `income` and `balance` in the multiple logistic regression model.
```{r}
boot.fn <- function(data,index){
    coef(glm(default ~ income + balance, family = "binomial", data = Default, subset = index))
}
```
**(c).**
Use the `boot()` function together with your `boot.fn()` function to estimate the standard errors of the logistic regression coefficients for `income` and `balance`.
```{r}
library(boot)
boot(Default,boot.fn,1000)
```
**The estimated standard errors for the coefficients associated with income and balance are** $4.946e-06$ and $2.277e-04$.

**(d).**
Comment on the estimated standard errors obtained using the `glm()` function and using your bootstrap function.

**The standard errors obtained from glm() and bootstrap are very close,so the bootstrap method is efficient.**

## Chapter 6

### Q1
We perform best subset, forward stepwise, and backward stepwise selection on a single data set. For each approach, we obtain p + 1 models, containing 0, 1, 2, . . . , p predictors. Explain your answers:

**(a).**Which of the three models with k predictors has the smallest training RSS?

* The smallest training RSS will be for the model with best subset approach. 

### Q8
In this exercise, we will generate simulated data, and will then use this data to perform best subset selection.
**(a)** Use the rnorm() function to generate a predictor X of length n = 100, as well as a noise vector $\epsilon$ of length n = 100.
```{r}
set.seed(123)
X = rnorm(100)
eps = rnorm(100)
```
**(b)** Generate a response vector Y of length n = 100 according to
the model $Y = \beta_{0} + \beta_{1}X + \beta_{2}X^{2} + \beta_{3}X^{3} + \epsilon$,
where $\beta_{0}, \beta_{1}, \beta_{2}, \beta_{3}$, are constants of your choice.
We select $\beta_{0} = 2, \beta_{1} = 4, \beta_{2} = -5, \beta_{3} = -1$
```{r}
Y = 3 + 4 * X + -5 * X^2 + -2* X^3 + eps
plot(X, Y)
```
**(c)** Use the regsubsets() function to perform best subset selection in order to choose the best model containing the predictors X,X2, . . .,X10. What is the best model obtained according to Cp, BIC, and adjusted R2? Show some plots to provide evidence for your answer, and report the coefficients of the best model obtained. Note you will need to use the data.frame() function to create a single data set containing both X and Y.
```{r}
library(leaps)
data.full = data.frame(y = Y, x = X)
model = regsubsets(y = Y,x = poly(X, 10, raw = T), nvmax = 10, method = "exhaustive")
model_summary = summary(model)
```

```{r}
plot(model_summary$cp, xlab="Subset Size", ylab="Best Subset Cp", type="l")
points(which.min(model_summary$cp), model_summary$cp[which.min(model_summary$cp)], col="blue", pch=2, lwd=3)
```
```{r}
plot(model_summary$bic, xlab="Subset Size", ylab="Best Subset BIC", type="l")
points(which.min(model_summary$bic), model_summary$bic[which.min(model_summary$bic)], col="blue", pch=2, lwd=3)
```
```{r}
plot(model_summary$adjr2, xlab="Subset Size", ylab="Best Subset AdjR2", type="l")
points(which.max(model_summary$adjr2), model_summary$adjr2[which.max(model_summary$adjr2)], col="blue", pch=2, lwd=3)
```
```{r}
model_summary$outmat
```
**Using Cp and BIC, the best size of subset is 3.**
```{r}
coef(model, id = 3)
```
**Using Adjusted R-Squared, the best size of subset is 7.**
```{r}
coef(model, id = 7)
```
**(d)** Repeat (c), using forward stepwise selection and also using backwards stepwise selection. How does your answer compare to the results in (c)?
Forward stepwise selection
```{r}
model = regsubsets(y = Y,x = poly(X, 10, raw = T), nvmax = 10, method = "forward")
model_summary = summary(model)
```

```{r}
plot(model_summary$cp, xlab="Subset Size", ylab="Best Subset Cp", type="l")
points(which.min(model_summary$cp), model_summary$cp[which.min(model_summary$cp)], col="blue", pch=2, lwd=3)
```

```{r}
plot(model_summary$bic, xlab="Subset Size", ylab="Best Subset BIC", type="l")
points(which.min(model_summary$bic), model_summary$bic[which.min(model_summary$bic)], col="blue", pch=2, lwd=3)
```
```{r}
plot(model_summary$adjr2, xlab="Subset Size", ylab="Best Subset AdjR2", type="l")
points(which.max(model_summary$adjr2), model_summary$adjr2[which.max(model_summary$adjr2)], col="blue", pch=2, lwd=3)
```
```{r}
model_summary$outmat
```
**Using Cp and BIC, the best size of subset is 4.**
```{r}
coef(model, id = 4)
```
**Using Adjusted R-Squared, the best size of subset is 5.**
```{r}
coef(model, id = 5)
```
Backwards stepwise selection
```{r}
model = regsubsets(y = Y,x = poly(X, 10, raw = T), nvmax = 10, method = "backward")
model_summary = summary(model)
```

```{r}
plot(model_summary$cp, xlab="Subset Size", ylab="Best Subset Cp", type="l")
points(which.min(model_summary$cp), model_summary$cp[which.min(model_summary$cp)], col="blue", pch=2, lwd=3)
```

```{r}
plot(model_summary$bic, xlab="Subset Size", ylab="Best Subset BIC", type="l")
points(which.min(model_summary$bic), model_summary$bic[which.min(model_summary$bic)], col="blue", pch=2, lwd=3)
```
```{r}
plot(model_summary$adjr2, xlab="Subset Size", ylab="Best Subset AdjR2", type="l")
points(which.max(model_summary$adjr2), model_summary$adjr2[which.max(model_summary$adjr2)], col="blue", pch=2, lwd=3)
```
```{r}
model_summary$outmat
```
Using Cp and BIC, the best size of subset is 3.
```{r}
coef(model, id = 3)
```
Using Adjusted R-Squared, the best size of subset is 7.
```{r}
coef(model, id = 7)
```
**Different selection methods and metrics result in different subsets of the predictors being selected. **

**(e)** Now fit a lasso model to the simulated data, again using X,X2,..., X10 as predictors. Use cross-validation to select the optimal value of λ. Create plots of the cross-validation error as a function of λ. Report the resulting coefficient estimates, and discuss the results obtained.
```{r}
library(glmnet)
set.seed(234)
xmat = model.matrix(y ~ poly(x, 10, raw = T), data = data.full)[, -1]
mod.lasso = cv.glmnet(xmat, Y, alpha = 1)
best.lambda = mod.lasso$lambda.min
best.lambda
```
```{r}
plot(mod.lasso)
```
```{r}
best.model = glmnet(xmat, Y, alpha = 1)
predict(best.model, s = best.lambda, type = "coefficients")
```
**Lasso also picks X1, X2, X7. It also picks X6, X7, X8, X9 with negligible coefficient.**

**(f)** Now generate a response vector Y according to the model Y = β0 + β7X7 + e, and perform best subset selection and the lasso. Discuss the results obtained.
We select $\beta_{0} = 2, \beta_{7} = 8$
```{r}
Y = 10 + 5*X^7 + eps
```
```{r}
data.full = data.frame(y = Y, x = X)
mod.full = regsubsets(y ~ poly(x, 10, raw = T), data = data.full, nvmax = 10)
mod.summary = summary(mod.full)
```
```{r}
which.min(mod.summary$cp)
```
```{r}
which.min(mod.summary$bic)
```
```{r}
which.min(mod.summary$adjr2)
```
```{r}
coefficients(mod.full, id = 1)
```
**We can see cp and BIC have the most accurate 1-variable model, but Adjust R2 pick additional variables.**
```{r}
xmat = model.matrix(y ~ poly(x, 10, raw = T), data = data.full)[, -1]
mod.lasso = cv.glmnet(xmat, Y, alpha = 1)
best.lambda = mod.lasso$lambda.min
best.lambda
```
```{r}
best.model = glmnet(xmat, Y, alpha = 1)
predict(best.model, s = best.lambda, type = "coefficients")
```
**We can see lasso also have the most accurate 1-variable model.**
