---
title: "PH.140.644_HW3"
author: "Kunyu An"
output:
  pdf_document:
    toc_depth: 2
    latex_engine : xelatex
  html_document:
    toc_depth: '2'
    df_print: paged
header-includes:
- \usepackage{amsmath,latexsym,amsfonts,amsthm,cleveref}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


```{r load_libraries,include=FALSE}
library(ISLR)
library(MASS) 
library(class)
```

## Chapter 10

### Q8
In Section 10.2.3, a formula for calculating PVE was given in Equation 10.8. We also saw that the PVE can be obtained using the `sdev` output of the `prcomp()` function.

On the  `USArrests` data, calculate PVE in two ways:

**(a)** Using the sdev output of the prcomp() function, as was done in
Section 10.2.3.
```{r}
attach(USArrests)
set.seed(1)
pr.out = prcomp(USArrests, scale=TRUE)
pr.var = pr.out$sdev^2
pve_1 = pr.var / sum(pr.var)
pve_1
```

**(b)** By applying Equation 10.8 directly. That is, use the prcomp() function to compute the principal component loadings. Then, use those loadings in Equation 10.8 to obtain the PVE.
```{r}
USArrests_scaled = scale( USArrests )
denom = sum( apply( USArrests_scaled^2, 2, sum ) )

Phi = pr.out$rotation
USArrests_projected = USArrests_scaled %*% Phi

numer = apply( pr.out$x^2, 2, sum )
pve_2 = numer / denom
pve_2
```

**As shown above, the result from (a) and (b) are the same.**

### Q9
Consider the `USArrests` data. We will now perform hierarchical clustering on the states.

**(a)** Using hierarchical clustering with complete linkage and Euclidean distance, cluster the states.
```{r}
set.seed(1)
hclust.complete = hclust( dist(USArrests), method="complete" )
plot(hclust.complete)
```

**(b)** Cut the dendrogram at a height that results in three distinct clusters. Which states belong to which clusters?
```{r}
ct = cutree( hclust.complete, 3 )
# Print which states go into each cluster
for( k in 1:3 ){
  print(k)
  print( rownames( USArrests )[ ct == k ] )
}
```

**(c)** Hierarchically cluster the states using complete linkage and Euclidean distance, after scaling the variables to have standard deviation one.
```{r}
scaled = scale(USArrests, center = FALSE)
hclust.complete.scale = hclust( dist(scaled), method="complete" )
plot(hclust.complete.scale)
```

**(d)** What effect does scaling the variables have on the hierarchical clustering obtained? In your opinion, should the variables be scaled before the inter-observation dissimilarities are computed? Provide a justification for your answer.
```{r}
ct = cutree( hclust.complete.scale, k=3 )
# Print which states go into each cluster
for( k in 1:3 ){
  print(k)
  print( rownames( USArrests )[ ct == k ] )
}
```

**Scaling the variables will affect the clusters. We should scale the variables since units of measure are very different.**

### Q11
On the book website, www.StatLearning.com, there is a gene expression data set (`Ch10Ex11.csv`) that consists of 40 tissue samples with measurements on 1,000 genes. The first 20 samples are from healthy patients, while the second 20 are from a diseased group.

**(a)** Load in the data using `read.csv()`. You will need to select `header=F`.
```{r}
genes = read.csv("Ch10Ex11.csv", header=FALSE)
head(genes)
```

**(b)** Apply hierarchical clustering to the samples using correlation- based distance, and plot the dendrogram. Do the genes separate the samples into the two groups? Do your results depend on the type of linkage used?
```{r}
plot(hclust(as.dist(1 - cor(genes)), method = "complete"))
plot(hclust(as.dist(1 - cor(genes)), method = "single"))
plot(hclust(as.dist(1 - cor(genes)), method = "average"))
```

**Based on the plots above, we can obtain two clusters for complete and single linkages or three clusters for average cluster.**

**(c)** Your collaborator wants to know which genes differ the most across the two groups. Suggest a way to answer this question, and apply it here.

**We can use PCA to determine which genes function best to illustrate the variance**

```{r}
pr.out <-  prcomp(t(genes))
summary(pr.out)
```
```{r}
total_load <-  apply(pr.out$rotation, 1, sum)
indices <-  order(abs(total_load), decreasing = TRUE)
indices[1:10]
total_load[indices[1:10]]
```

**Above shows the top 10 genes which are most distinct from others**